Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-06 Tex/Old text/chapters/introduction.tex
revised Section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

While some existing research efforts do aim enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. Among the opportunities for enhancements in the development processes for CPS software, there exists the need to develop new techniques and tools to support CPS requirement gathering and analysis to synthesize \textit{correct-by-construction} implementations of CPS. These techniques have to deal with predefined requirements enforced by nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with by formal verification~\cite{NESSI}.

Among the many CPS systems, in this thesis we will focus specifically on energy generation by stand-alone solar PV systems. The lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below the 1 billion threshold for the first time in 2017~\cite{IEAweo2018}. The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}. Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}. 
Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}. It follows that, increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.

The use of the power generation technology with renewable energy sources is developing rapidly due to the industrial development~\cite{Yatimi}. Renewable energy leads to advances all over the world by protecting the environment: it is clean (low greenhouse gas emissions), operates silently, long-lasting, low maintenance costs, zero fuel costs and an  inexhaustible supply~\cite{Noroozian}. Renewable energy, and particularly power generated from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.

@@

Moreover, the optimum sizing of these devices is essential for reliable operation. Therefore, these systems need to be designed in accordance with the site, the land area available, load requirement, load pattern, environmental conditions, and economics in order to utilize available resources efficiently and economically~\cite{Rawat}.

@@

Energy access is an important issue because it can put together economic growth, human development and environmental sustainability. Energy has long been recognized as essential for humanity to develop and thrive, but the adoption in 2015 by 193 countries of a goal to ensure access to affordable, reliable, sustainable and modern energy for all by 2030, as part of the new United Nations Sustainable Development Goals (SDGs), marked a new level of political recognition~\cite{IEAweo2018}.

The International Energy Agency (IEA) revealed that from 2000 to 2016 nearly all of those who gained access to electricity worldwide did so through new grid connections, mostly with power generation from fossil fuels. Over the last five years, however, renewable sources have started to gain ground, as have off-grid and mini-grid systems. By 2030, renewable energy sources power over 60\% of new access, and off-grid and mini-grid systems provide the means for almost half of new access~\cite{IEAweo2018}. Moreover, if we focus into the Amazonas State, Brazil, where around 5\% of the population in 2018 were isolated in 2,261 communities (or 41,167 houses), without electrical energy or even road access, using just boats by rivers, therefore energy is a very important issue.

Under this scenario, it is important to have very well designed PV systems that won't fail when installed in the field and at the lowest acquisition cost possible.

In order to address different aspects of a solar PV project, there is a variety of public domain and commercial software solutions  available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general-purpose simulation tools such as PSpice, and the MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}. According to~\cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation to site survey and system design tools, and to sophisticated financial analysis software (with optimization). Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.  
%
Manufacturers and integrators also have their own proprietary software to perform system sizing~\cite{Zhou2010}, with the drawback of indicating only their own products among the possibilities of choice, which restricts their solution. 
%
%PV systems can be classified into grid-connected and stand-alone systems. At this proposal, only off-grid or stand-alone systems will be considered. The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.  
However, public domain and commercial software and even proprietary tools are based on running experiments in simulation models. Simulation has the advantage of being cheap (if compared to testing in real systems) and can be employed before the system design is concluded. However, it has the drawback of an incomplete coverage since the verification of all possible combinations, and of potential system failures is unfeasible~\cite{ClarkeHV18}.

@@

Model-based verification techniques are based on models that describe possible system behavior in a mathematically precise, and unambiguous manner. Thus, problems such as incompleteness, ambiguities, and inconsistencies, which are generally discovered only in the later stages of the design, can be detected in advance, as described by \cite{Trindade,TrindadeDJISC17}. 
Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the given system meets the requirements.
%
%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
%

%automated synthesis
Optimization of PV systems is not a recent topic; since the $1990$s different techniques have been developed and evaluated using a wide variety of criteria to find the ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods~\cite{Applasamy2011}. The ideal combination for  any PV system is made by the best compromise between two considered objectives, which are \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.

However, formal methods based on \textit{symbolic model checking} applied to synthesize PV systems have not been further explored in the literature, which could offer a great opportunity to obtain a more effective design process for PV systems~\cite{ClarkeHV18}.

@@

The main objective of this thesis is thus to prove that is possible to use formal verification method to validate the design and to use formal synthesis method to optimize the sizing of stand-alone solar PV systems. Secondarily, we aim to develop two tools written in ANSI-C and platform-independent, based on the the new proposed techniques in order to evaluate different state-of-the art symbolic software verifiers (and solvers), and comparing the experimental results with simulation tool and with data from real PV systems installed in riverside communities. Always evaluating correctness and performance.

@@

%More specifically we will:
%The thesis produces a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
The originality of this thesis lies in the creation of an automated verification technique to solar PV systems. The research led to the creation of two software solutions to carry out computational experiments and to compare with commercial tools and real data from systems installed in the field. One software solution to perform automated verification and validate the solar PV systems behavior, the other to produce the optimal sizing of solar PV systems through an automated synthesis program.

@@

The proposed technique is applied by means of an algorithm implemented using the C programming language. We performed computing experimentation in three state-of-the-art model checkers to formally verify PV designs, aiming to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
%three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}. %, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.

With respect to the \textbf{automated synthesis} technique and optimal sizing of stand-alone PV systems, this thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input. Given a correctness specification $\sigma$, the proposed method uses $\sigma$ as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$ with respect to power reliability. In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, which may not attain the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted. If it fails, then a counterexample is provided with an optimal sizing that meets power reliability and system cost requirements. Note that in this study, the focus is not on new criteria or even optimization objectives. Instead, the novelty lies in the practical approach to the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tools.

Simply put, we aim to present new techniques that will ensure that you have good designs of stand-alone solar PV systems, that do not cause a drop in energy supply, and that these systems are designed at the lowest possible cost.

@@

Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system and optimal sizing. Validation when a sized system must be evaluated in order to decide if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or when the user tries to obtain a better solution that he or she has. We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in a comparison with specialized simulation tools, supported by real data from installed PV systems.

%Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system and optimal sizing. Validation when a sized system must be evaluated in order to define if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or then the user tries to obtain a better solution that he or she has. We thus develop algorithms and the corresponding tools; moreover, we evaluate them with several case studies, in a comparative with specialized simulation tools, supported by real data from deployed PV systems.
Fig.\ref{fig:validation_outline} outlines the proposed solution to perform the validation of stand-alone solar PV systems via automated verification. Fig.\ref{fig:optimization_outline} illustrates the proposed solution to obtain the optimal sizing of stand-alone solar PV systems via automated synthesis. We pictured here only a summary of each phase of our proposed approach, highlighting the input parameters, the outputs for the validation, or the optimal size of the solar PV system; more details will be presented in the next chapters. Moreover, the illustrations show the methodological approach with respect to comparative result analysis, employing our approaches, the commercial software tool, and data from real PV systems deployed in the field.

@@

With respect to the proposed \textbf{automated verification} technique, this thesis makes three main contributions: \textbf{first}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; \textbf{second}, we evaluate the verification technique by comparing three state-of-the-art model checkers in five real case studies; \textbf{third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.

@@

% Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers. Secondly
%
%With respect to the proposed \textbf{automated verification} method, this thesis makes three main contributions. 
%\textbf{First}, we propose an algorithm written in the C programming language, which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system. \textbf{Second}, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies. \textbf{Third}, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation. 
%
%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
%
%And linked to \textbf{automated synthesis}, our work makes more three original contributions: \textbf{First}, it is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems; \textbf{Secondly}, we propose a variant CEGIS method of synthesis with striking differences of how the {\sc Synthesize} and {\sc Verify} phases from original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and \textbf{Thirdly}, experimental results with seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tool: our solution is far detailed and closer to real PV systems than the solution presented by simulation.
%
%three major contributions. 
%\textbf{First}, the use of automated symbolic verification methods in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with the user requirements and environment constraints, and the proposed synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. 
%\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in the verification back-end for synthesizing optimal PV systems, thereby being the first work that performs this type of evaluation. 
%\textbf{Third}, the experimental results show that the proposed synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool. As a result, this thesis marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems. Thus, this research considerably advances the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.

@@

In this section we discuss only the use of formal methods in electrical systems in general since optimization of PV sizing is currently not obtained by formal methods or even program synthesis. %Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.

@@

Another study from $2018$ presented an approach to modeling smart grid components using a formal specification. The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}. The formal specification presented can be considered a first step towards modeling smart grids using formal methods. The starting point of this study was that a smart home can be considered an integrated system consisting of various objects and systems, which communicate and interact with each other. This approach is based on Petri nets and works under the assumption that modeling smart homes leads to a clear understanding of the overall behavior of the smart grids.

However, prior studies did not deal with formal verification of a complete stand-alone PV system (with batteries, charge controller, and power inverter) or even solar PV systems optimization. Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in the literature. Moreover, it is precisely on these gaps that this thesis is focused.

@@

This introduction has outlined the context, motivation, and problem addressed by this thesis and the objectives, solution, and contributions of the research. The remaining chapters are organized as follows:

@@

In the `~\nameref{chap:conclusions}' we present the main contributions, future work directions and concluding remarks.

@@

~\autoref{chap:tools} depicts the tools created during the Ph.D process to implement and validate the two scientific methods of the thesis (and instructions for their use).

~\autoref{chap:data} presents detailed data from all the equipment used during the experimental part of the thesis, covering information from data-sheet, electrical features, brands and models.

It is worth mentioning that we decided, with the consent of the coordination of the graduate program, that this document would be written in the active voice and entirely in English. The choice of the active voice comes from the choice of the English language, which in the thesis studied was always presented in the active voice. The decision to use the English language stems from the possibility that the research may lead to further developments and activities,  in the possibility of reaching a larger number of people and helping in the internationalization of the Federal University of Amazonas.

>>>>

While some existing research efforts do aim to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. Among the opportunities for enhancements in the development processes for CPS software, there exists the need to develop new techniques and tools to support CPS requirement gathering and analysis to synthesize \textit{correct-by-construction} implementations of CPS. These techniques have to deal with predefined requirements enforced by nature and inherited constraints of the target CPS. Besides, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with by formal verification~\cite{NESSI}.

Among the many CPS systems, in this thesis, we will focus specifically on energy generation by stand-alone solar PV systems. The lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Nevertheless, the world is progressing; in particular, the number of people without electricity access fell below the 1 billion thresholds for the first time in 2017~\cite{IEAweo2018}. The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}. Numbers from Brazil show the aim to electrify 270 isolated areas and 2.7 million people by 2023~\cite{EPE2018}. 
Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}. It follows that increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}.

The use of power generation technology with renewable energy sources is developing rapidly due to industrial development~\cite{Yatimi}. Renewable energy leads to advances all over the world by protecting the environment: it is clean (low greenhouse gas emissions), operates silently, long-lasting, low maintenance costs, zero fuel costs and an inexhaustible supply~\cite{Noroozian}. Renewable energy, and particularly power generated from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.

@@

Moreover, the optimum sizing of these devices is essential for reliable operation. Therefore, these systems need to be designed under the site, the land area available, load requirement, load pattern, environmental conditions, and economics in order to utilize available resources efficiently and economically~\cite{Rawat}.

@@

Energy access is an essential issue because it can put together economic growth, human development, and environmental sustainability. Energy has long been recognized as essential for humanity to develop and thrive, but the adoption in 2015 by 193 countries of a goal to ensure access to affordable, reliable, sustainable and modern energy for all by 2030, as part of the new United Nations Sustainable Development Goals (SDGs), marked a new level of political recognition~\cite{IEAweo2018}.

The International Energy Agency (IEA) revealed that from 2000 to 2016, nearly all of those who gained access to electricity worldwide did so through new grid connections, mostly with power generation from fossil fuels. Over the last five years, however, renewable sources have started to gain ground, as have off-grid and mini-grid systems. By 2030, renewable energy sources power over 60\% of new access, and off-grid and mini-grid systems provide the means for almost half of new access~\cite{IEAweo2018}. Moreover, if we focus on the Amazonas State, Brazil, where around 5\% of the population in 2018 was isolated in 2,261 communities (or 41,167 houses), without electrical energy or even road access, using just boats by rivers, therefore energy is a fundamental issue.

Under this scenario, it is crucial to have very well designed PV systems that will not fail when installing in the field and at the lowest acquisition cost possible.

In order to address different aspects of a solar PV project, there is a variety of public domain and commercial software solutions available, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general-purpose simulation tools such as PSpice, and the MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}. According to~\cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation to site survey and system design tools, and sophisticated financial analysis software (with optimization). Some tools also provide support to rebate program applications and tax incentives (specific to each country or region). In contrast, other programs and worksheets focus on the technical aspects of system sizing and design.  
%
Manufacturers and integrators also have their proprietary software to perform system sizing~\cite{Zhou2010}, with the drawback of indicating only their products among the possibilities of choice, which restricts their solution. 
%
%PV systems can be classified into grid-connected and stand-alone systems. At this proposal, only off-grid or stand-alone systems will be considered. The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.  
However, public domain and commercial software and even proprietary tools are based on running experiments in simulation models. Simulation has the advantage of being cheap (if compared to testing in real systems) and can be employed before the system design is concluded. However, it has the drawback of incomplete coverage since the verification of all possible combinations, and potential system failures are unfeasible~\cite{ClarkeHV18}.

@@

Model-based verification techniques are based on models that describe possible system behavior in a mathematically precise, and unambiguous manner. Thus, problems such as incompleteness, ambiguities, and inconsistencies, which are generally discovered only in the later stages of the design, can be detected in advance, as described by \cite{Trindade,TrindadeDJISC17}. 
Model-checking algorithms can then verify the system model by systematically exploring all its states to check whether the given system meets the requirements.
%
%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
%

%automated synthesis
Optimization of PV systems is not a recent topic; since the $1990$s different techniques have been developed and evaluated using a wide variety of criteria to find the ultimate combinations for design parameters based on intuitive, numerical, and analytical methods~\cite{Applasamy2011}. The ideal combination for any PV system is made by the best compromise between two considered objectives, which are \textit{power reliability} and \textit{system cost}~\cite{Alsadi2018}.

However, formal methods based on \textit{symbolic model checking} applied to synthesize PV systems have not been further explored in the literature, which could offer an excellent opportunity to obtain a more effective design process for PV systems~\cite{ClarkeHV18}.

@@

The main objective of this thesis is thus to prove that it is possible to use a formal verification method to validate the design and to use a formal synthesis method to optimize the sizing of stand-alone solar PV systems. Secondarily, we aim to develop two tools written in ANSI-C and platform-independent, based on the new proposed techniques to evaluate different state-of-the-art symbolic software verifiers (and solvers). We also aim to compare the experimental results with the simulation tool and with data from real PV systems installed in riverside communities, thereby evaluating correctness and performance.

@@

%More specifically we will:
%The thesis produces a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.
The originality of this thesis lies in the creation of an automated verification technique for solar PV systems. The research led to the creation of two software solutions to carry out computational experiments and to compare with commercial tools and real data from systems installed in the field. One software solution to perform automated verification and validate the solar PV systems behavior, the other to produce the optimal sizing of solar PV systems through an automated synthesis program.

@@

The proposed technique is applied through an algorithm implemented using the C programming language. We employed three state-of-the-art model checkers to verify PV designs formally, thus aiming to evaluate performance and correctness. The C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
%three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}. %, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.

Concerning the \textbf{automated synthesis} technique and optimal sizing of stand-alone PV systems, this thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input. Given a correctness specification $\sigma$, the proposed method uses $\sigma$ as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$ for power reliability. In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, which may not attain the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted. If it fails, then a counterexample is provided with an optimal sizing that meets power reliability and system cost requirements. Note that in this study, the focus is not on new criteria or even optimization objectives. Instead, the novelty lies in the practical approach to the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tools.

\textbf{ We aim to present new techniques that will guarantee a good design of stand-alone solar PV systems, that do not cause a drop in energy supply after deployment, and that these systems are designed at the lowest possible cost.}

@@

Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems to tackle two issues: validation of a designed system and optimal sizing. Validation when a sized system must be evaluated in order to decide if it meets the design requirements and user needs. \textcolor{red}{this sentence is confusing... Optimization, when there exist just the requirements and the PV system, is not sized, or when the user tries to obtain a better solution that he or she has}. We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in comparison with specialized simulation tools, supported by real data from installed PV systems.

%Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems in order to tackle two issues: validation of a designed system and optimal sizing. Validation when a sized system must be evaluated in order to define if it meets the design requirements and user needs; and optimization when there are just the requirements and the PV system is not sized, or then the user tries to obtain a better solution that he or she has. We thus develop algorithms and the corresponding tools; moreover, we evaluate them with several case studies, in a comparative with specialized simulation tools, supported by real data from deployed PV systems.
Fig.~\ref{fig:validation_outline} outlines the proposed solution to perform the validation of stand-alone solar PV systems via automated verification. Fig.\ref{fig:optimization_outline} illustrates the proposed solution to obtain the optimal sizing of stand-alone solar PV systems via automated synthesis. We pictured here only a summary of each phase of our proposed approach, highlighting the input parameters, the outputs for the validation, or the optimal size of the solar PV system; more details will be presented in the next chapters. Moreover, the illustrations show the methodological approach concerning comparative result analysis, employing our approaches, the commercial software tool, and data from real PV systems deployed in the field.

@@

\textcolor{red}{The following two paragraphs are too long! Please consider breaking them into smaller sentences!}

Concerning the proposed \textbf{automated verification} technique, this thesis makes three main contributions: \textbf{first}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; \textbf{second}, we evaluate the verification technique by comparing three state-of-the-art model checkers in five real case studies; \textbf{third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.

@@

% Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers. Secondly
%
%With respect to the proposed \textbf{automated verification} method, this thesis makes three main contributions. 
%\textbf{First}, we propose an algorithm written in the C programming language, which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system. \textbf{Second}, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies. \textbf{Third}, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation. 
%
%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
%
%And linked to \textbf{automated synthesis}, our work makes more three original contributions: \textbf{First}, it is the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems; \textbf{Secondly}, we propose a variant CEGIS method of synthesis with striking differences of how the {\sc Synthesize} and {\sc Verify} phases from original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and \textbf{Thirdly}, experimental results with seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tool: our solution is far detailed and closer to real PV systems than the solution presented by simulation.
%
%three major contributions. 
%\textbf{First}, the use of automated symbolic verification methods in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with the user requirements and environment constraints, and the proposed synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. 
%\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in the verification back-end for synthesizing optimal PV systems, thereby being the first work that performs this type of evaluation. 
%\textbf{Third}, the experimental results show that the proposed synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool. As a result, this thesis marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems. Thus, this research considerably advances the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.

@@

In this section, we discuss only the use of formal methods in electrical systems in general since the optimization of PV sizing is currently not obtained by formal methods or even program synthesis. %Here we discuss only the use of formal methods on electrical systems in general since currently there exists no use of it or even program synthesis to obtain the optimization of PV sizing.

@@

Another study from $2018$ presented an approach to modeling smart grid components using a formal specification. The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}. The formal specification presented can be considered a first step towards modeling smart grids using formal methods. The starting point of this study was that a smart home could be considered an integrated system consisting of various objects and systems, which communicate and interact with each other. This approach is based on Petri nets and works under the assumption that modeling smart homes lead to a clear understanding of the overall behavior of the smart grids.

However, prior studies did not deal with formal verification of a complete stand-alone PV system (with batteries, charge controller, and power inverter) or even solar PV systems optimization. Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in the literature. Moreover, it is precisely on these gaps that this thesis is focused on.

@@

This introduction has outlined the context, motivation, and problem addressed by this thesis and the objectives, solutions, and contributions of the research. The remaining chapters are organized as follows:

@@

In the `~\nameref{chap:conclusions}', we present the main contributions, future work directions and concluding remarks.

@@

~\autoref{chap:tools} depicts the tools created during the Ph.D. process to implement and validate the two scientific methods of the thesis (and instructions for their use).

~\autoref{chap:data} presents detailed data from all the equipment used during the experimental part of the thesis, covering information from data-sheet, electrical features, brands, and models.

It is worth mentioning that we decided, with the consent of the coordination of the graduate program, that this document would be written in the active voice and entirely in English. The choice of the active voice comes from the choice of the English language, which in the thesis studied was always presented in the active voice. The decision to use the English language stems from the possibility that the research may lead to further developments and activities, in the possibility of reaching a more significant number of people and helping in the internationalization of the Federal University of Amazonas.
